Model for categorical choice scenarios (experiments 4 to 6)

### 2023-11-08 Experiment_4/model.Rmd
Remove cached *_files directories

```{r, message=FALSE, echo=FALSE}
# Load packages
library(tidyverse)
library(gghalves) # for plots
library(patchwork)
library(lme4) # for linear mixed models
library(lmerTest) # p-values for mixed models
library(broom) # for tidy outputs of regressions
library(broom.mixed) # for tidy outputs of linear mixed models
```

```{r, echo=FALSE}
#set general theme for plots
plot_theme <- theme_minimal(base_size = 12) +
  theme(# Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold axis titles
        axis.title = element_text(face = "bold"))
```

@@

We assume that individuals (i) vary in competence and (ii) that competence that it is distributed uniformly in the population.

@@

```{r}
# 4: identify constellations 
data <- data %>% 
  # identify how often a one type of answer occurs in one group
  group_by(sample_id, answer) %>% 
  mutate(n_answer_in_sample = n()) %>% 
  # assign constellations
  group_by(sample_id) %>% 
  mutate(unique_answers = n_distinct(answer),
         # Build a first version of constellation variable
         constellation = case_when(unique_answers == sample ~ "dissensus", 
                                   unique_answers == 1 ~ "consensus",
                                   unique_answers <  sample ~ "majority"
         ),
         # identify minority answers in majority constellations
         minority = ifelse(constellation == "majority", 
                           # report whether occurences of answer within a group
                           # are the minority within that group
                           n_answer_in_sample == min(n_answer_in_sample),
                           # for all other constellations, simply code NA,
                           NA
         ), 
         # identify majority answers in majority constellations
         majority = ifelse(constellation == "majority", 
                           # report whether occurrences of answer within a group
                           # are the majority within that group
                           n_answer_in_sample == max(n_answer_in_sample),
                           # for all other constellations, simply code NA,
                           NA
         ), 
         # modify the constellation variable to distinguish between minority, 
         # intermediate majority, majority and dissensus that is composed of 
         # multiple answers (e.g. 3 options, sample of 6, two per option)
         constellation = case_when(
           is.na(minority) | is.na(majority) ~ constellation, 
           minority == TRUE & majority == TRUE ~ "dissensus",
           minority == TRUE ~ "minority", 
           majority == TRUE ~ "majority", 
           .default = "intermediate majority")
  ) %>% ungroup()
```

@@

# compute the summary statistics by constellation
results <- data %>% 
  group_by(constellation) %>% 
  summarize(average_competence = mean(competence), 
            average_relative_competence = mean(relative_competence),
            average_accuracy = mean(accurate)) %>% 
  # store simulation information
  mutate(population = population, 
         sample = sample, 
         options = options)
```

@@

```{r, echo=FALSE}
simulate_single_population <- function(population, sample, options, 
                                       distribution = "uniform", 
                                       return = "summarized") {
  # Check if population is not divisible by sample without remainder
  if (population %% sample != 0) {
    warning("Population is not divisible by sample without remainder.")
  }

@@

  if (distribution == "uniform") {
  # randomly draw competence levels
  data <- tibble(id = 1:population,
                 competence = runif(population, min = 1/options, max = 1))
  }

  if (distribution == "normal") {
  # randomly draw competence levels
  data <- tibble(id = 1:population,
                 competence = rnorm(population, mean = 0.6, sd = 0.01))
  }

@@

  # 4: identify constellations 
  data <- data %>% 
    # identify how often a one type of answer occurs in one group
    group_by(sample_id, answer) %>% 
  mutate(n_answer_in_sample = n()) %>% 
    # assign constellations
  group_by(sample_id) %>% 
    mutate(unique_answers = n_distinct(answer),
           # Build a first version of constellation variable
           constellation = case_when(unique_answers == sample ~ "dissensus", 
                                     unique_answers == 1 ~ "consensus",
                                     unique_answers <  sample ~ "majority"
           ),
           # identify minority answers in majority constellations
           minority = ifelse(constellation == "majority", 
                             # report whether occurences of answer within a group
                             # are the minority within that group
                             n_answer_in_sample == min(n_answer_in_sample),
                             # for all other constellations, simply code NA,
                             NA
           ), 
           # identify majority answers in majority constellations
           majority = ifelse(constellation == "majority", 
                             # report whether occurrences of answer within a group
                             # are the majority within that group
                             n_answer_in_sample == max(n_answer_in_sample),
                             # for all other constellations, simply code NA,
                             NA
           ), 
           # modify the constellation variable to distinguish between minority, 
           # intermediate majority, majority and dissensus that is composed of 
           # multiple answers (e.g. 3 options, sample of 6, two per option)
           constellation = case_when(
             is.na(minority) | is.na(majority) ~ constellation, 
             minority == TRUE & majority == TRUE ~ "dissensus",
             minority == TRUE ~ "minority", 
             majority == TRUE ~ "majority", 
             .default = "intermediate majority")
           ) %>% ungroup()

@@

  # compute the summary statistics by constellation
  results <- data %>% 
    group_by(constellation) %>% 
    summarize(average_competence = mean(competence), 
              average_relative_competence = mean(relative_competence),
              average_accuracy = mean(accurate),
              count = n_distinct(sample_id)) %>% 
    # store simulation information
    mutate(population = population, 
           sample = sample, 
           options = options)

  if(return == "summarized") {
    return(results)
  } else {
    return(data)
  }
}

```

```{r, echo=FALSE}
# # test output (set return to data above)
# test <- simulate_single_population(population = 600, sample = 6, options = 3, 
#                                    return = "raw data") %>% arrange(sample_id)
# levels(as.factor(test$constellation))
# 
# test %>% filter(constellation == "intermediate majority")
```

@@

vary_sample_options <- function(vary = "options", file_name, n, ...) {

@@

      # do the `calculate_power()` function for each sample size and store the results
      # in a new variable called `power`
      data <- n %>% purrr::map_df(function(n_option){
                                     # this is essentially a for loop - 
                                     # do the following for each 
                                     # element data$n_subj

@@

                                     # run power calculation
                                     result <- simulate_various_populations(
                                       options = n_option, ...)

@@

@@

      write_csv(data, paste0("data/", file_name))
    }
  }
}
```

@@

  # make constellation a factor with the right levels
  d$constellation <- fct_relevel(d$constellation, "minority", "dissensus", "intermediate majority", "majority", "consensus")

  # extract simulation info
  simulation_info <- d %>% summarize(across(c(population, sample, options, total_iterations), mean)) %>% 
    pivot_longer(everything(), names_to = "parameter", values_to = "value") %>% 
    gridExtra::tableGrob(cols = NULL, rows = NULL)

  # make descriptive data
  descriptive <- d %>% 
    group_by(constellation) %>% 
    summarise(count = sum(count)) %>% 
    mutate(rel_freq = round(count / sum(count), digits = 2)) %>% 
    gridExtra::tableGrob(rows = NULL)

@@

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y =  average_relative_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence") +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    ylim(c(0, 1))

  # unite tables
  tables <- gridExtra::grid.arrange(descriptive, simulation_info, ncol = 2)

@@

    return((plot_accuracy | plot_competence) / tables)
  }

@@

    return(plot_accuracy)
  }

@@

  # make constellation a factor with the right levels
  d$constellation <- fct_relevel(d$constellation, "minority", "dissensus", "intermediate majority", "majority", "consensus")

@@

@@

### Fixed sample and choice options

```{r}
file_name <- "model_3_sample_3_options.csv" # change for new analyses / or delete file to re-use same name

@@

# read simulated data from .csv files
data_3 <- read_csv(paste0("data/", file_name))

# descriptive
data_3 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))
```

#### Plot

```{r}
plot_results(data_3)
plot_accuracy_model <- plot_results(data_3, outcome = "accuracy")
plot_competence_model <- plot_results(data_3, outcome = "competence")
```

#### Analyze

```{r, echo=FALSE}
# possible analysis
regression_data <- data_3 %>%
  mutate(
    # make numeric version of convergence
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1 
  )

accuracy_model <- lm(average_accuracy ~ convergence, 
                     data = regression_data)
competence_model <- lm(average_relative_competence ~ convergence, 
                       data = regression_data)

```

### Varying sample and choice options

### Generate data

# run simulation and store results in .csv files
vary_sample_options(n = n, vary = "options", iterations = 1000, population = 999, sample = 3, file_name = "model_vary_options_3_sample.csv")
vary_sample_options(n = n, vary = "sample", iterations = 1000, population = 999, options = 3, file_name = "model_vary_sample_3_options.csv")

# read simulated data from .csv files
data_3_options <- read_csv("data/model_vary_options_3_sample.csv")
data_3_sample <- read_csv("data/model_vary_sample_3_options.csv")

```

### Plot

```{r, echo=FALSE}
# plot results
plot_results_vary(data_3_options)
plot_results_vary(data_3_sample, variable = sample)
```

### Analyze

```{r, echo=FALSE}
# possible analysis
regression_data <- data_3_options %>% 
  filter(options %in% c(3, 10)) %>% 
  group_by(iteration, constellation, options) %>% 
  summarise(across(c(average_accuracy, average_relative_competence), mean)) %>% 
  mutate(
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    options = as.factor(options), 
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1
  )

accuracy <- lm(average_accuracy ~ convergence + options + convergence*options, 
               data = regression_data) 
competence <- lm(average_relative_competence ~ convergence + options, data = regression_data)

## Compare model vs. participants

@@

### Table

@@

# model for accuracy
# random intercept and slope by participants
accuracy_participants <- lmer(accuracy ~ convergence + (1 + convergence | id), 
                                 data = d)
# model for competence
# random intercept and slope by participants
competence_participants <- lmer(competence ~ convergence + 
                           (1 + convergence | id), data = d)
```

```{r, echo=FALSE}
# main result table
modelsummary::modelsummary(list("Accuracy" = accuracy_participants, 
                                "Competence" = competence_participants,
                                "Accuracy" = accuracy_model, 
                                "Competence" = competence_model
                                ),
                           title = 'Participants vs. Model', 
                           stars = TRUE) %>%
  kableExtra::add_header_above(c(" " = 1, "Participants" = 2, "Model" = 2))
```

### Plots

#### Participant data

```{r, echo=FALSE}
# plot for accuracy
plot_accuracy <- ggplot(d,
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, echo=FALSE}
# plot for competence
plot_competence <- ggplot(d,
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

#### Combine participant and model

```{r, echo=FALSE}
# accuracy
plot_accuracy <- plot_accuracy + ggtitle("Participants")
plot_accuracy_model <- plot_accuracy_model + ggtitle("Model")

@@

>>>>

```{r, message=FALSE, echo=FALSE}
# Load packages
library(tidyverse)
library(gghalves) # for plots
library(patchwork)
library(lme4) # for linear mixed models
library(lmerTest) # p-values for mixed models
library(broom) # for tidy outputs of regressions
library(broom.mixed) # for tidy outputs of linear mixed models
library(ggpubr) # for plots
```

```{r, echo=FALSE}
# set general theme for plots
plot_theme <- theme_minimal(base_size = 12) +
  theme(# Bold title
    plot.title = element_text(face = "bold", size = rel(0.7)),
    # Plain subtitle that is grey
    plot.subtitle = element_text(face = "plain", size = rel(1), color = "grey70"),
    # Bold legend titles
    legend.title = element_text(face = "bold"),
    # Bold axis titles
    axis.title = element_text(face = "bold"), 
    # Bold legend labels
    legend.text = element_text(face = "bold")
    )
```

@@

We assume that individuals (i) vary in competence and (ii) that the distribution of competence in the population varies, as can be modeled by a beta distribution. In the case below, we assume a uniform competence distribution (equal to a beta distribution of alpha = 1 and beta = 1).

@@

```{r}
# 4: identify constellations 
data <- data %>% 
  # identify how often a one type of answer occurs in one group
  group_by(sample_id, answer) %>% 
  mutate(n_answer_in_sample = n()) %>% 
  # assign constellations
  group_by(sample_id) %>% 
  mutate(unique_answers = n_distinct(answer),
         # Build a first version of constellation variable
         constellation = case_when(unique_answers == 1 ~ "consensus",
                                   unique_answers <=  sample ~ "majority-minority-dissensus"
         ),
         # identify majority answers in majority constellations
         majority = ifelse(constellation == "majority-minority-dissensus", 
                           # report whether occurrences of answer within a group
                           # are the majority within that group
                           n_answer_in_sample == max(n_answer_in_sample),
                           # for all other constellations, simply code NA,
                           NA
         ), 
         # identify dissensus answers in majority constellations
         dissensus = ifelse(constellation == "majority-minority-dissensus", 
                            # report whether occurrences of answer within a group
                            # are the minority within that group
                            min(n_answer_in_sample) == max(n_answer_in_sample),
                            # for all other constellations, simply code NA,
                            NA
         ), 
         # build final constellation variable using helper variables 
         constellation = case_when(
           dissensus == TRUE ~ "dissensus",
           majority == TRUE ~ "majority",
           majority == FALSE ~ "minority(ies)",
           .default = constellation)
  ) %>% ungroup()
```

@@

# compute the summary statistics by sample id
results <- data %>% 
  group_by(sample_id, constellation) %>% 
  summarize(average_competence = mean(competence), 
            average_relative_competence = mean(relative_competence),
            average_accuracy = mean(accurate)) %>% 
  # store simulation information
  mutate(population = population, 
         sample = sample, 
         options = options)
```

@@

```{r, echo=FALSE}
simulate_single_population <- function(population, sample, options, 
                                       distribution = "uniform", 
                                       alpha, beta,
                                       return = "by constellation") {
  # Check if population is not divisible by sample without remainder
  if (population %% sample != 0) {
    warning("Population is not divisible by sample without remainder.")
  }

@@

  if (distribution == "uniform") {
  # randomly draw competence levels
    data <- tibble(id = 1:population,
                   competence = runif(population, min = 1/options, max = 1)) %>% 
      # Create a relative measure of competence that allows to compare across
      # different numbers of choice options. 
      # This measure varies from 0 = random chance to 1 = definitely right. 
      # We use min-max scaling, with min = 1/options and max = 1.
      mutate(relative_competence = (competence - 1/options) / (1 - 1/options))
  }

  if (distribution == "beta") {
  # randomly draw competence levels
  data <- tibble(id = 1:population,
                 relative_competence = rbeta(population, shape1 = alpha, 
                                             shape2 = beta)) %>% 
    mutate(
      competence = relative_competence * (1 - 1/options) + 1/options
      )
  }

@@

  # 4: identify constellations 
  data <- data %>% 
    # identify how often a one type of answer occurs in one group
    group_by(sample_id, answer) %>% 
  mutate(n_answer_in_sample = n()) %>% 
    # assign constellations
  group_by(sample_id) %>% 
    mutate(unique_answers = n_distinct(answer),
           # relative degree of majority
           n_sample = n_distinct(id),
           relative_majority = n_answer_in_sample / n_sample,
           # Build a first version of constellation variable
           constellation = case_when(unique_answers == 1 ~ "consensus",
                                     unique_answers <=  sample ~ "majority-minority-dissensus"
           ),
           # identify majority answers in majority constellations
           majority = ifelse(constellation == "majority-minority-dissensus", 
                             # report whether occurrences of answer within a group
                             # are the majority within that group
                             n_answer_in_sample == max(n_answer_in_sample),
                             # for all other constellations, simply code NA,
                             NA
           ), 
           # identify dissensus answers in majority constellations
           dissensus = ifelse(constellation == "majority-minority-dissensus", 
                             # report whether occurrences of answer within a group
                             # are the minority within that group
                             min(n_answer_in_sample) == max(n_answer_in_sample),
                             # for all other constellations, simply code NA,
                             NA
           ), 
           # build final constellation variable using helper variables 
           constellation = case_when(
             dissensus == TRUE ~ "dissensus",
             majority == TRUE ~ "majority",
             majority == FALSE ~ "minority(ies)",
             .default = constellation)
           ) %>% ungroup()

@@

  if(return == "by participant") {
    return(data)
  } else {

    if(return == "by degree of majority") {
      results <- data %>% 
        group_by(sample_id, relative_majority)
    }

    if(return == "by constellation") {
      results <- data %>% 
        group_by(sample_id, constellation)
    }

    # compute the summary statistics by sample id (and constellation)
    results <- results %>% summarize(average_competence = mean(competence), 
                                     average_relative_competence = mean(relative_competence),
                                     average_accuracy = mean(accurate),
                                     count = n_distinct(sample_id)) %>% 
      # store simulation information
      mutate(population = population, 
             sample = sample, 
             options = options)

    return(results)
  }
}
```

```{r, echo=FALSE}
# test output (set return to data above)
# test <- simulate_single_population(population = 10000, sample = 10, options = 10,
#                                    return = "by degree of majority", distribution = "beta",
#                                    alpha = 2, beta = 6) %>% arrange(sample_id) %>%
#   arrange(sample_id)
# 
# test %>% group_by(relative_majority) %>% summarise(across(c(average_relative_competence,
#                                                         average_accuracy),
#                                                       mean)
#                                                )
```

@@

vary_sample_options <- function(vary = "options", file_name, n, 
                                format = "result", ...) {

@@

      # run the populations generating function for different values of n
      data <- n %>% purrr::map_df(function(n_option){
        # this is essentially a for loop - 
        # do the following for each 
        # element of n

@@

        # run simulation
        result <- simulate_various_populations(
          options = n_option, ...)

@@

      if(format == "result") {
        return(data)
      } else{
        write_csv(data, paste0("data/", file_name))
      }
    }

@@

      if(format == "result") {
        return(data)
      } else{
        write_csv(data, paste0("data/", file_name))
      }
    }
  }
}
```

#### Vary competence distribution

We now want to do the above (simulate a single population, repeat this process, do so for various sample sizes and choice options) for different competence distributions. We vary these distributions with the `alpha` and `beta` parameters for the beta distributions.

vary_competence <- function(file_name, alpha, beta, names, ...) {

    competence_data <- tibble(alpha, beta, names) %>% 
      mutate(competence = paste0(names, "\n(alpha = ", alpha, ", beta = ", beta, ")"))

    # do all the above functions for different competence distributions
    data <- competence_data$competence %>% purrr::map_df(function(competence_level){
      # this is essentially a for loop

      # To keep track of progress
      print(paste("competence_level = ", competence_level))

      # set alpha and beta
      alpha = competence_data %>% filter(competence == competence_level) %>% pull(alpha)
      beta = competence_data %>% filter(competence == competence_level) %>% pull(beta)

      # run simulation
      result <- vary_sample_options(
        alpha = alpha, beta = beta, file_name = file_name, ...)

      # add competence level
      result <- result %>% mutate(competence = competence_level, 
                                  alpha = alpha,
                                  beta = beta)

    write_csv(data, paste0("data/", file_name))
  }
}
```

@@

  # make constellation a factor with the right levels
  d$constellation <- fct_relevel(d$constellation, "minority(ies)", "dissensus", "majority", "consensus")

  # extract simulation info
  simulation_info <- d %>% summarize(across(c(population, sample, options, total_iterations), mean))

  caption = paste0("Number of choice options: ", simulation_info$options,
                   "; Sample size: ", simulation_info$sample,
                   "; Iterations : ", simulation_info$total_iterations, 
                   "; Population size per iteration: ", simulation_info$population)

  # make descriptive data
  # descriptive <- d %>% 
  #   group_by(constellation) %>% 
  #   summarise(count = sum(count)) %>% 
  #   mutate(rel_freq = round(count / sum(count), digits = 2)) %>% 
  #   gridExtra::tableGrob(rows = NULL)

@@

  # plot for competence
  plot_competence <- ggplot(d,
                            aes(x = constellation, y =  average_relative_competence, fill = constellation)) +
    geom_half_violin(position = position_nudge(x = -.2),
                     adjust=2, alpha = .8,
                     side = "l") +
    stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
    stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
    stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
    # Add nice labels
    labs(x = "Convergence", y = "Competence", caption = caption) +
    scale_fill_viridis_d(option = "plasma", begin = 0.1) +
    guides(fill = FALSE) +
    plot_theme + 
    theme(axis.text.x = element_text(angle = 20, hjust = 1)) +
    ylim(c(0, 1))

  # unite tables
  # tables <- gridExtra::grid.arrange(descriptive, simulation_info, ncol = 2)

@@

    return(plot_accuracy | plot_competence )
  }

@@

    return(plot_accuracy + labs(caption = caption))
  }

@@

  # make constellation a factor with the right levels
  d$constellation <- fct_relevel(d$constellation, "minority(ies)", "dissensus", "majority", "consensus")

@@

#### c) Plot varying competence distributions

Third, we want a function that plots results by various competence levels.

```{r}
plot_competence_vary <- function(data, variable = options, outcome = "Accuracy", 
                                 return = "simulations") {

  # retrieve info from choice of variable
  if (variable_name == "options") {
    x_label = "Number of Choice Options"
    caption = paste0("Sample size of informants: ", d$sample[1],
                     "; Iterations per sample size: ", d$total_iterations[1], 
                     "; Population size per iteration: ", d$population[1])
  }
  if (variable_name == "sample") {
    x_label = "Size of informant groups"
    caption = paste0("Number of choice options: ", d$options[1],
                     "; Iterations per sample size: ", d$total_iterations[1], 
                     "; Population size per iteration: ", d$population[1])
  }

  # make constellation a factor with the right levels
  d$constellation <- fct_relevel(d$constellation, "minority(ies)", "dissensus", "majority", "consensus")

  d <- d %>% 
    group_by(constellation, {{variable}}, competence) %>% 
    summarise(competence_mean = mean(average_relative_competence),
              accuracy_mean = mean(average_accuracy),
              accuracy_sd = sd(average_accuracy),
              competence_sd = sd(average_relative_competence)
    )

  # Assign outcome variable
  if(outcome == "Accuracy") {
    d$outcome <- d$accuracy_mean
    d$outcome_sd <- d$accuracy_sd
  }

  if(outcome == "Competence") {
    d$outcome <- d$competence_mean
    d$outcome_sd <- d$competence_sd
  }

  # plot for accuracy
  plot_outcome <- ggplot(d,
                         aes(x = {{variable}}, y = outcome,
                             color = constellation)) +
    # geom_half_violin(position = position_nudge(x = -.2),
    #                  adjust=2, alpha = .5,
    #                  side = "l") +
    geom_pointrange(aes(ymin = outcome - outcome_sd, 
                        ymax = outcome + outcome_sd), 
                    size = 0.1) +
    geom_line() +
    # Add nice labels
    labs(x = x_label, y = outcome, caption = caption) +
    scale_color_viridis_d(option = "plasma", begin = 0.1, 
                          limits = rev(levels(d$constellation)),
                          direction = -1
    ) +
    facet_wrap(~competence) +
    plot_theme + 
    theme(legend.position = "top")

  # Plot competence distributions
  # Your data frame
  d <- data %>% 
    group_by(competence) %>% 
    reframe(alpha = unique(alpha), beta = unique(beta))

  # Function to plot the different competence distributions 
  plot_competence_distributions <- function(alpha, beta) {
    ggplot() +
      geom_function(
        fun = ~dbeta(.x, shape1 = alpha, shape2 = beta)
      ) +
      labs(title = paste0("alpha = ", alpha, ", beta = ", beta), 
           y = "Density", x = "Competence") +
      plot_theme
  }

  # Specify the values of alpha and beta from the data
  alpha_values <- d$alpha
  beta_values <- d$beta

  # Create a list of ggplot objects
  plot_list <- map2(alpha_values, beta_values, plot_competence_distributions)

  # Arrange and display the plots
  competence_plot <- ggarrange(plotlist = plot_list) %>%
    ggpubr::annotate_figure(top = ggpubr::text_grob("Competence distributions", 
                                                    face = "bold",
                                                    color = "darkgrey",
                                                    size = 14))

  if(return == "competence distributions") {
    return(competence_plot)
  } else {
   return(plot_outcome) 
  }
} 
```

#### d) Plot varying competence distributions by relative majority

Fourth, we want another function that plots results by various competence levels - but this time not for  constellations but the numeric value of the relative majority.

```{r}
plot_competence_vary_relative_majority <- function(data, variable = options, outcome = "Accuracy") {

  # retrieve info from choice of variable
  if (variable_name == "options") {
    caption = paste0("Sample size of informants: ", d$sample[1],
                     "; Iterations per sample size: ", d$total_iterations[1], 
                     "; Population size per iteration: ", d$population[1])
  }
  if (variable_name == "sample") {
    caption = paste0("Number of choice options: ", d$options[1],
                     "; Iterations per sample size: ", d$total_iterations[1], 
                     "; Population size per iteration: ", d$population[1])
  }

  d <- d %>% 
    group_by(relative_majority, {{variable}}, competence) %>%
    summarise(competence_mean = mean(average_relative_competence),
              accuracy_mean = mean(average_accuracy),
              accuracy_sd = sd(average_accuracy),
              competence_sd = sd(average_relative_competence)
    )

  # Assign outcome variable
  if(outcome == "Accuracy") {
    d$outcome <- d$accuracy_mean
    d$outcome_sd <- d$accuracy_sd
  }

  if(outcome == "Competence") {
    d$outcome <- d$competence_mean
    d$outcome_sd <- d$competence_sd
  }

  plot_outcome <- ggplot(d, 
                         aes(x = relative_majority, y = outcome,
                             color = as.factor({{variable}}))) +
    geom_point() +
    geom_line() +
    # Add nice labels
    labs(x = "Relative majority \n (share of informants agreeing on an option)", 
         y = outcome, caption = caption, 
         color = variable_name) +
    scale_color_viridis_d(option = "plasma", begin = 0.1, 
                          #limits = rev(levels(d$constellation)),
                          direction = -1
    ) +
    facet_wrap(~competence) +
    plot_theme + 
    theme(legend.position = "top")

   return(plot_outcome)

#### e) Plot competence

Finally, we want to plot the underlying competence distributions

```{r}
# Plot competence distributions
plot_competence_distributions <- function(data) {
  # Your data frame
  d <- data %>% 
    group_by(competence) %>% 
    reframe(alpha = unique(alpha), beta = unique(beta))

  # Function to plot the different competence distributions 
  plot_competence_distributions <- function(alpha, beta) {
    ggplot() +
      geom_function(
        fun = ~dbeta(.x, shape1 = alpha, shape2 = beta)
      ) +
      labs(title = paste0("alpha = ", alpha, ", beta = ", beta), 
           y = "Density", x = "Competence") +
      plot_theme
  }

  # Specify the values of alpha and beta from the data
  alpha_values <- d$alpha
  beta_values <- d$beta

  # Create a list of ggplot objects
  plot_list <- map2(alpha_values, beta_values, plot_competence_distributions)

  # Arrange and display the plots
  competence_plot <- ggarrange(plotlist = plot_list) %>%
    ggpubr::annotate_figure(top = ggpubr::text_grob("Competence distributions", 
                                                    face = "bold",
                                                    color = "darkgrey",
                                                    size = 14))

  return(competence_plot) 
}
```

@@

```{r}
# Tryout beta functions
# ggplot() +
#   geom_function(fun = ~dbeta(.x, shape1 = 0.9, shape2 = 0.9))
```

### Experiment 4

#### Generate Data

First, we want to simulate data under assumptions that correspond to our experimental design.

For the first, simulation, we fix all parameters. We assume:
- a uniform competence distribution (beta = 1 and alpha = 1)
- 3 choice options,
- samples of 3 (i.e. 3 informants)

We generate a sample of 999x1000 = 999000 individuals.

```{r, message=FALSE}
file_name <- "sim_experiment_4.csv" # change for new analyses / or delete file to re-use same name

@@

# read simulated data from .csv files
sim_experiment_4 <- read_csv(paste0("data/", file_name))
```

#### Plot result

We make then make a plot corresponding to the figure from the experiments.

```{r}
# descriptive
sim_experiment_4 %>% group_by(constellation) %>% summarise(across(c(average_accuracy, average_competence), mean))

plot_results(sim_experiment_4)
```

#### Analyze data

```{r, echo=FALSE}
# possible analysis
regression_data <- sim_experiment_4 %>%
  mutate(
    # make numeric version of convergence
    convergence = case_when( 
      constellation == "minority" ~ 0, 
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3), 
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1 
  )

accuracy_model <- lm(average_accuracy ~ convergence, 
                     data = regression_data)
competence_model <- lm(average_relative_competence ~ convergence, 
                       data = regression_data)
```

#### Compare participants and simulations

@@

##### Table

@@

# model for accuracy
# random intercept and slope by participants
accuracy_participants <- lmer(accuracy ~ convergence + (1 + convergence | id), 
                                 data = d)
# model for competence
# random intercept and slope by participants
competence_participants <- lmer(competence ~ convergence + 
                           (1 + convergence | id), data = d)

# main result table
modelsummary::modelsummary(list("Accuracy" = accuracy_participants, 
                                "Competence" = competence_participants,
                                "Accuracy" = accuracy_model, 
                                "Competence" = competence_model
                                ),
                           title = 'Participants vs. Model', 
                           stars = TRUE) %>%
  kableExtra::add_header_above(c(" " = 1, "Participants" = 2, "Model" = 2))
```

##### Plots

```{r, echo=FALSE}
# Participant data

# plot for accuracy
plot_accuracy <- ggplot(d,
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

# plot for competence
plot_competence <- ggplot(d,
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r}
# Model data
plot_accuracy_model <- plot_results(sim_experiment_4, outcome = "accuracy")
plot_competence_model <- plot_results(sim_experiment_4, outcome = "competence")
```

```{r, echo=FALSE}
# Combine participant and model
# accuracy
plot_accuracy <- plot_accuracy + ggtitle("Participants")
plot_accuracy_model <- plot_accuracy_model + ggtitle("Model")

@@

### Experiment 6

In experiment 6, we varied choice options (from 3 to 10).

In this simulation, we assume:
- a sample size of 3 
- a uniform competence distribution (beta = 1 and alpha = 1)

# run simulation and store results in .csv files
vary_sample_options(n = n, format = "csv file", vary = "options", iterations = 5, population = 10000, 
                    sample = 3, file_name = "sim_vary_options_3_sample.csv", 
                    distribution = "beta", alpha = 1, beta = 1)

# read simulated data from .csv files
data_3_options <- read_csv("data/sim_vary_options_3_sample.csv")
```

#### Plot result

```{r}
# example for plot
plot_results_vary(data_3_options, 
                  variable = options)
```

#### Analyze data

```{r, echo=FALSE}
# possible analysis for varying choice options (3 vs. 10)
regression_data <- data_3_options %>%
  filter(options %in% c(3, 10)) %>%
  # group_by(iteration, constellation, options) %>%
  # summarise(across(c(average_accuracy, average_relative_competence), mean)) %>%
  mutate(
    convergence = case_when(
      constellation == "minority" ~ 0,
      constellation == "dissensus" ~ 1,
      constellation == "majority" ~ 2,
      constellation == "consensus" ~ 3),
    options = as.factor(options),
    # scale accuracy to reach from 0 to 100 (instead from 0 to 1)
    average_accuracy = average_accuracy*100,
    # scale competence to reach from 1 to 7 (instead of 0 to 1)
    average_relative_competence = 6*average_relative_competence + 1
  )
